Rubin Observatory Pointing Algorithm and Survey Simulation

### 2025-02-05 ms.tex
Updates from Overleaf

>>>>

\begin{figure}
\epsscale{0.5}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvis_scheduler_note_like_DD_HEAL_SkyMap.pdf}
\plotone{plots/tiers/baseline_v4_0_10yrs_Nvisits_as_function_of_Alt_Az_scheduler_note_like_DD_HEAL_SkyMap.pdf}
\plotone{plots/tiers/run_name_Hourglass_scheduler_note_like_DD_and_night_lt_730_HOUR_Hourglass.pdf}
\epsscale{1}
\caption{Distribution of DDF observations \label{fig:tiers_ddf}}
\end{figure}
